Bayesian Reconstruction of Coevolutionary Histories

### 2013-09-25 paper/article.tex
General progress

% Acronyms
\acrodef{GTR}{general time reversible}
\acrodef{MCMC}{Markov chain Monte Carlo}

@@

@@

@@

\paragraph*{Case study: cycad--weevil}

@@

@@

@@

>>>>

% Acronyms
\acrodef{GMTC}{geographic mosaic theory of coevolution}
\acrodef{GTR}{general time reversible}
\acrodef{MCMC}{Markov chain Monte Carlo}

@@

Finally, I apply

@@

\paragraph*{Case study: cycad--weevil coevolution}

@@

\paragraph*{Cycad--weevil coevolution.}

@@

A important question from the biological perspective is, how fine a scale ?

In research on gopher--louse

One of the inherent challenges with the cycad--weevil dataset was .

Some cophylogeny reconstruction programs, such as Jane \parencite{Conow:2010}, consider the \enquote{} event

The greater takeaway, however, is that to to perform a complete, cophylogenetic analysis on a datset

@@

I discussed . \textcite{Yang:2010} developed a Bayesian \ac{MCMC} methodology to determine the species delimitations between a set of individuals. Maintaining

@@

\ac{GMTC} . Ultimately, it may be possible , and thus to test the \ac{GMTC} against coevolutionary histories.
